---
title: "Homework 3 - Part 2"
output:
  pdf_document: default
  html_document:
    theme: cerulean
date: 'Due: Oct 9th by 11:59 pm'
---

<br/>

Each year since 2005, the US Census Bureau surveys about 3.5 million households with The [American Community Survey](https://www.census.gov/programs-surveys/acs/) (ACS). Data collected from the ACS have been crucial in government and policy decisions, helping to determine the allocation of more than $400 billion in federal and state funds each year. For example, funds for the Adult Education and Family Literacy Act are distributed to states taking into consideration data from the ACS on number of adults 16 and over without a high school diploma. This act is the primary source of federal funding for adults with low basic skills seeking further education or English language services, and Department of Education uses ACS data to ensure the efficient distribute funds.

The ACS received a surge of media attention in Spring 2012 when the House of Representatives voted to eliminate the survey.  Daniel Webster, a first-term Republican congressman from Florida, sponsored the legislation citing the following reasons:  

- "This is a program that intrudes on people's lives, just like the Environmental Protection Agency or the bank regulators" 
- "We're spending \$70 per person to fill this out. That's just not cost effective"
- "in the end this is not a scientific survey. It's a random survey."

In this assignment you will create "useful" visualizations using data from the ACS.

<br/>

### Accessing the data

The data can be found in the `openintro` package.

If you are running RStudio locally you will need to install the package from CRAN, install this package:

```{r eval=FALSE}
install.packages("openintro")
```

once it is installed, you can load the package with

```{r echo=FALSE, message=FALSE}
library(openintro)
library(ggplot2)
library(dplyr)
```

and load the data with

```{r echo=FALSE}
data(acs12)
```

It is a good idea to take a look at the codebook for the data which can be found the in `acs12` help file, which can be accessed using

```{r eval=FALSE}
?acs12
```

or at https://www.rdocumentation.org/packages/openintro/versions/1.7.1/topics/acs12.

<br/>

### Assignment

<br/>

#### 1. Data properties

<i>As a team, browse the data and select *three* variables that you think are interesting and that you think may have an interesting relationship. 

For each of the variables you selected answer the following question: What are some of the properties of these variables that will be relevant (useful? problematic?) for data visualization? You are welcomed to include univariate visualizations to your answer, but you don't have to.</i>

<!-- Write up here -->

```{r}


acs12 <- na.omit(acs12)
acs12$age_group<-acs12$age
acs12$age_group[acs12$age_group>=65]<-"over 60"
acs12$age_group[acs12$age_group<65& acs12$age_group>=45]<-"45~60"
acs12$age_group[acs12$age_group<45& acs12$age_group>=25]<-"30~45"
acs12$age_group[acs12$age_group<25& acs12$age_group>=18]<-"18~30"
acs12$age_group[acs12$age_group<18]<-"below 18"
acs12$age_group <- factor(acs12$age_group, levels = c("below 18","18~30","30~45","45~60","over 60"))
acs12$gender <- factor(acs12$gender, levels = c("female","male"))

acs12_sub<-acs12[acs12$income!=0,]

p<-quantile(acs12$income,probs=0.75,na.rm=TRUE)
acs12_top25<-acs12[acs12$income>p,]

j<-acs12_top25 %>% 
  select(gender,age_group) %>%
  group_by(gender,age_group) %>%
  summarize(percent = n()/nrow(na.omit(acs12_top25)))


```

```{r}
ggplot(acs12, aes(x = income)) + 
  geom_density() +
  theme_bw()
```

We are interested in exploring the relationship between income, age, and gender. More specifically, we would like to investigate the distribution of income by age and income. The distribution of income presents challenges for visualization as it is highly positively skewed with a range that spans several orders of magnitude. Therefore, in order for our visualizations to be more effective, we log transform income. We note, however, that we must exclude all observations for which income is zero so that this transformation can be applied. Thus, our analysis is only concerned with the distribution of income for those who are employed (i.e. have non-zero income).

Age is particular conducive to visualization as it can be treated as a continous variable, or can be discretized so as to consider differences in income across age groups depending on the objective of the visualization. We use the latter in our analysis as we are concerned with investigating general differences in income across age brackets rather than more granular quantities such as the marginal effect of age on income.

Gender will be used to investigate whether the relationship betwen income and age implied by our visualizations varies between men and women.



<br/>

#### 2. Plots

Select and design two different plots that visualize the relationship between these three variables. Each plot should have a different "purpose" that guides your choices and justifies the differences between the plots.


```{r plot1}
library(ggplot2)
ggplot(acs12_sub,aes(x=age_group,y=log(income))) +
  geom_boxplot(aes(x=age_group,y=log(income),fill=gender)) +
  theme_bw() +
  labs(x = "Age group", y = "Log(Income)", colour = "Gender",
       title = "Distirubtion of Income by Age and Gender")
```

```{r plot2}
ggplot(j,aes(x=age_group,y=percent,fill=gender,label=percent))+
  geom_bar(stat = "identity") +
  theme_bw() +
  geom_text(data=j, aes(label=paste0(round(percent*100,1),"%"),
                               y=percent+0.012), size=3,position = position_stack(vjust = 0.5)) +
  labs(x = "Age group", y = "Percent", colour = "Gender",
       title = "Percent of Top Quantile of Earners by Age and Gender")
```


<br/>

#### 3. Plot properties

What two plot types have you selected? What are some of the properties of these plots, and how do those properties match with your variables of interest?

\
Answer: We selected boxplot and bar graph. Properties of boxplot: show the distribution of data (mean, quantile, outliers). Properties of bar graph: show the numbers of cases within each group. We want to look at how income varies with gender and age, so the boxplot is a perfect fit for this purpose; as for the bar graph, we chose it because we want to look at among the top 25% person that have highest incomes, how many males and females are there in each age group.

We select a boxplot and bar graph to visualize the distribution of income by age group subsetted by gender, and the demographics of the top quartile of earners, respectively. 

The comparative boxplots show the median, quartiles, and outliers within each group and thus is optimal for displaying the differences in income across age groups. Furthermore, subsetting each age group by gender enables us not only to see if the distribution of income between men and women varies within each age group but also if there is a difference in the change in income across age groups, by gender.

The stacked bar graph enables us to visualize the makeup of the top quartile of earners by age and gender. The comparative boxplots show the distribution of income across age groups, by gender, and does not take into account the relative size of the populations of each subgroup. The bar graph does incorporate this information and allows us to visualize who makes up the top quartile of earners. We accomplish this by looking at the relative size of each age group in the top quartile of the income distribution and by subsetting each age group by gender.

<br/>

#### 4. Tasks

<i>Think of who the target audience might be for your plots. What task(s) should users of each plot be able to undertake? Why are these tasks important for these variables?</i>

\
Answer: 

The objective of these plots is to convey differences in the distribution of income by age group and gender, and to describe the makeup of the distribution of high earners, respectively. The comparative boxplots would be of interest to those who want to learn about the general differences in the distribution of income across age groups, by gender. The stacked bar graph would be of interest to those concerend about unequal representation of women in the top 25% of earners.

Those who view the comparative boxplots should be able to decipher the differences in income across age groups, and the differences between men and women within each group, at a cursory glance. Namely, the plot shows that the median male income is higher than the median female income across all age groups. Moreover, the plot indicates that the median income for both men and women increases by age group - excluding the over 60 group. With more careful inspection they should be able to uncover that changes in the income distributions across age groups are not as severe for women, as they are for men. For example, the increase in the median income for men from 18-30 to 30-45 is larger than the increase in the median income for women across these groups.

Those who view the stacked bar graph should clearly see that the population of high earners is almost entirely composed of those in the age groups 30-45 and 45-60. Moreover, viewers should see that the population of high earners is predominately male.

<br/>

#### 5. Design context

<i>Describe how the design choices you made help the users accomplish the intended task(s).</i>

The structure comparative boxplots is conducive to the comparisons we sought to highlight and thus very little explicit design choices were necessary in order to effectively convey the information contained in the plot. We discretized the age groups in accordance with a division commonly used by the Census Bureau. While this step is rather arbitrary it does allow for the effective display of the data without crowding the plot.

The structure of the stacked bar graph clearly lets users compare the relative representations of the age groups in the top quartile of earners. Furthermore, it is evident that men outnumber women within each of these age groups. However, it is not clear from the bar graph alone what the relative contributions of each subgroup to the population of top earners. That is, while we can clearly read off what percent of top earners are between the age of 30-45, we cannot, at a glance, determine what percent of top earners are women between the ages of 30-45. Thus, we add labels to each section of the stacked bar graph to faciliate a comparison across subgroups. 

<br/>

#### 6. User skills

<i>What type of audience did you intend the plots for? What types of skills does this audience bring to the understanding of your plots? What elements of your plots might be difficult for the audience to understand, and how do you justify the choices you have made about those elements?</i>

Both of these plots are intended for those with public policy interest but little background in formal statistics. This audience should be familiar with the summary information contained in the comparative boxplots and thus should be able to use them to draw inferences about the differences in the distribution of income across age groups, by gender. Little to no requiste knowledge of statistics is needed in order to glean information regarding the top quartile of earners from the stacked bar graph

We did not group by gender and then subset by age as the resulting visualizaiton did not display the information as clearly as grouping by age group then subsetting by gender. 
As mentioned previously, we chose to use log(income) instead of income because the range of income from the sample was too broad -- without transforming income it would be hard to remove outliers or to figure out the patterns.

<br/>